Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
paper: add implementation table
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/overview.png}
\caption{A Ceph installation consists of a cluster running mostly
storage daemons (OSDs) to ensure data durability, a few monitor daemons
(MONs) to reach consensus of the cluster state and to ensure its
consistent versioning, and a few metadata service daemons (MDSs) for
scalable metadata service. Ceph's APIs include object, block, file
abstractions. Malacology enables the programmability of these
abstractions and services. To illustrate Malacology we implement two
services on Ceph, Zlog and Mantle, by programming Ceph's durability,
consistent versioning, consensus, and metadata subsystems.
\label{fig:overview}}
\end{figure}

@@

\section{Services Built on
Malacology}\label{services-built-on-malacology}

\label{services}

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Cap Owner & Failure & ZLog Recovery \\ \hline
mds & mds & mds \\ \hline
client & mds & xfer client cap \\ \hline
mds & client & n/a \\ \hline
client & client & mds \\
\hline
\end{tabular}
\caption{Failure and recovery scenarios.}
\label{t:mds-zlog-fail}
\end{table}

>>>>

\begin{figure}[tb]
\centering
\includegraphics{figures/overview.png}
\caption{A Ceph installation consists of a cluster running mostly
storage daemons (OSDs) to ensure data durability, a few monitor daemons
(MONs) to reach consensus of the cluster state and to ensure its
consistent versioning, and a few metadata service daemons (MDSs) for
scalable metadata service. Ceph's APIs include object, block, file
abstractions. Malacology enables the programmability of these
abstractions and services. To illustrate Malacology we implement two
services on Ceph, Zlog and Mantle, by programming Ceph's durability,
consistent versioning, consensus, and metadata subsystems.
\label{fig:overview}}
\end{figure}

@@

@@

\section{Services Built on Malacology}\label{services-built-on-malacology}
\label{services}

\begin{table}
\centering
\begin{tabular}{  l | l | l    }
\textbf{Service} & \textbf{Ceph Component} & \textbf{Used for...}  \\ \hline
Mantle  & RADOS    & policy durability \\
        & MON maps & policy versioning \\ \hline
ZLog    & Logical Storage & CORFU protocol  \\ 
        & MON maps & interface install \\ \hline
Seq.    & MDS file types & log management \\ 
        & MDS fault toler. & seq. fault toler. \\
\end{tabular}
\caption{To implement the Mantle and ZLog services, we leverage Ceph components. Malacology uses these subsystems because they provide powerful abstractions.}
\label{table:implementation}
\end{table}
